---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ussie

<!-- badges: start -->
[![R-CMD-check](https://github.com/cpenaloza/ussie/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/cpenaloza/ussie/actions/workflows/R-CMD-check.yaml)
[![test-coverage](https://github.com/cpenaloza/ussie/actions/workflows/test-coverage.yaml/badge.svg)](https://github.com/cpenaloza/ussie/actions/workflows/test-coverage.yaml)
<!-- badges: end -->

The goal of ussie is to explore the European League Football data back from 1880 something. 

## Installation

You can install the development version of ussie from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("cpenaloza/ussie")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(ussie)
germany <- uss_make_matches(engsoccerdata::germany, "Germany")
germany2 <- uss_make_matches(engsoccerdata::germany2, "Germany2")

```

\
\

### What does our data look like?
```{r glimpsedata}
dplyr::glimpse(germany)
```

\
\

### Let's plot that!
```{r germany, echo = FALSE}

library(ggplot2)
library(magrittr)

germany %>% 
  dplyr::bind_rows(., germany2)  %>% 
  ggplot(aes(season, country)) +
  geom_boxplot()

```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
